A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-02-18 docs/paper/fsuthesis/thesis-template/paper.tex
finished TaintScope paper

TODO [T] TaintScope [AB]

>>>>

This general scheme is accomplished with fine-grained dynamic taint analysis, that is, taint analysis at the byte level, as opposed to a more general boolean level of taint, where perhaps user input is tainted and all non-user input is untainted. As fuzzers evolve they appear to favor more and more finely-grained taint analysis.

TaintScope implements DTA using PIN to instrument syscalls in binaries. PIN\_AddSyscallEntryFunction and PIN\_AddSyscallExitFunction are used to monitor syscalls which are known to introduce taint to a system, such as open, which might open a user-specified file, or read, which might read user-defined bytes into memory. Taint is followed as it propogates throughout data via move instructions and arithmetic instructions. TaintScope's tainting policy however, transfers taint by unioning taint values whenver they both appear in an instruction. Thus, if the policy is enforced strictly, and eax and ebx were both tainted, mov eax, ebx would regard eax as now tainted with both eax and ebx, when in reality the value of ebx has been moved into eax, removing the original taint from eax. This is one example of overtainting, which should be taken into account to achieve acceptable performance. Note also that, as of the paper, TaintScope does not take into account control-flow dependencies when tracking taint [T].

DTA is used to identify the so-called "hot bytes", which are then used as symbolic values later on, should test cases warrant further attention because of a crash or other interesting behavior. This strategy has netted TaintScope 27 new vulnerabilities across several different pieces of software, most of which operate on complicated file format specifications like PNG or PCAP files [T].
